---
title: March 7, 2017 - Pre-Class
date: '2017-03-02'
slug: march-7-2017-pre-class
categories:
  - Pre-Class
  - R
tags:
  - Github
  - R
  - Functions
---






# Further Github Page Setup


## Set up Disqus

1. Go to [Disqus](https://disqus.com)
2. Sign in with your e-mail. 
3. Add Disqus to your site by filling out this [form](https://disqus.com/admin/create/)


**Note: You will then receive a shortname**

4. Go into your github page and place the shortname in the `config.toml` file. 


## Load In Class lab from February 28, 2017

You can actually add your lab in as a post on your website. 

1. Click on the `addins` button right below the menus and above your markdown window. 
2. Click `New Post`
3. Name this post: `February 28, 2017 - In-Class Project`
4. Copy the contents from your lab into this and make sure you have completed all of the functions. 
5. Save the changes to this document and run:
```
blogdown::build_course()
```
6. Now push the changes to your github page and make sure the project displays on your webpage.






# Further R Functions Practice

It is crucial to make sure we have a strong foundation with R Functions. In order to make sure of this we will be extending out function creation and debugging another week. Here is what you will accomplish:

- More Function Tutorials/Practice
- The start of a lab for this week. 

As you start this assignment, please comment below with your github username so that I can let everyone know whose github pages to go to. 

## Functions Practice for this Week

1. Complete the DataCamp assignment you have received. 
2. Make sure you have read the [DataCamp Functions Tutorial](https://www.datacamp.com/community/tutorials/functions-in-r-a-tutorial#gs.lva4hyE)
3. Read the [Functions Chapter](http://r4ds.had.co.nz/functions.html) in [R For Data Science](http://r4ds.had.co.nz/)
4. Complete the practice from below and load it on your website as a new post by ***Monday, March 6, 2017 at 12:00pm***




## Pre Class Project:

[Markdown File Here](https://github.com/php2560/preclass/blob/master/2017-03-02-march-7-2017-pre-class.Rmd)




### Jackknife of the Mean!

- Have an estimator $\hat{\theta}$ of parameter $\theta$  
  want the standard error of our estimate, $se_{\hat{\theta}}$
- The jackknife approximation:
    + omit case $i$, get estimate $\hat{\theta}_{(-i)}$
    + Take the variance of all the $\hat{\theta}_{(-i)}$
    + multiply that variance by $\frac{(n-1)^2}{n}$ to get $\approx$ variance of $\hat{\theta}$
- then $se_{\hat{\theta}}=$ square root of that variance

<small>(Why $(n-1)^2 / n$?  Think about just getting the standard
    error of the mean)</small>



Write a function called `mean.jackknife` that takes argument `a_vector` and returns a jackknife estimate of the standard error.


```{r, eval=FALSE}
mean.jackknife <- function(a_vector) {
  # Put your function in here
  return(jackknife.stderr)
}
```



## Jackknife for the mean Example: test your code here


```{r, eval = FALSE}
some_normals <- rnorm(100,mean=7,sd=5)
mean(some_normals)
(formula_se_of_mean <- sd(some_normals)/sqrt(length(some_normals)))
all.equal(formula_se_of_mean,mean.jackknife(some_normals))
```

